Improving practices in a small french company: first step

### 2019-11-19 article.tex
complete moving average definition

\section{Related Work}\label{sec:related-work}
Research about software defect model for the reliable prediction of post-release defects in software is an ongoing and yet unresolved research topic. It was already discussed in multiple  publications \cite{Catal09,Hall2012, Hoss2017}. 
Steffen Herbold \cite{Herb19} propose a cost model for software defect prediction
These models aims to predict post-release defects but our model aims to fit  defects dataset  in order our reengineering on the studied system.   
\section{Defect Model}\label{sec:defectModel}
\subsection{Moving average}
A moving average is a statistic technic usually used to smooth a time serie data. Let $ (t_1,y_1) , (t_2,y_2) , . . ., (t_n,y_n) $ a time serie  where
\begin{equation*} SMA_{n}=\frac{1}{n}\sum\nolimits_{t=k-n+1}^{k}A_{t}\tag{1} \end{equation*}
\subsection{Presentation of the studied system}
In general, legacy systems have a lifespan of several decades, decisions made at the beginning of development and their evolution over the life of the software are often lost. 
This is the case of the studied system  which has a life cycle of  more than 20 years. 
It has 3 MLOC software written in Powerbuilder. With 117 Powerbuilder library, the  bigest library is  over 300 KLOC.
The system is not versioned and old versions are lost until 2012.

@@

 \subsection{Experimentations}
For each problem, we experiement on the ticket database. 
\subsubsection{Avoid the system souce code lost}
The system source code is not versioned.  Some versions of the system are lost. 
When developers work in the same version of the system, they chat with each other to notify which part of the system they are modifying so that others won't modify the same part to avoid losing modifications. Besides, each developer has to write in a comment in the source code his name and the date in the form of each modification he made.  We believe that writing author in a comment in the source can be easily handled by a version control system.
This is because of Powerbuilder support version controlling system from the 2017 release. 
The support provided by Powerbuilder is not stable.
The conflict resolution option is limited and a simple copy-paste of a library require a huge walkaround to update files. 
With this constraint, we chose to start with a simple to use version controlling system. We introduce Apache Subversion. 
 \subsubsection{Number of defects per library}
We plot  defects and evolution per library over time.  In x axis we have years and in y axis  we have the number of defects  or evolutions.
This give us an overview of defect  history per library. And  which libraries   trend to have defects.
\subsubsection{ Average time to open and close a ticket}
A ticket is closed when the task it is related to is done and validated. 
We use the time a ticket remains open over the life cycle of the studied system as an indicator of the system state. 
We grouped tickets by the month of creation.
We then compute the average of  the duration between the time when the ticket is created and the time when the ticket is closed for each month.  
We do this for tickets categorized as defect and tickets categorized as evolution. 
We finally plot the result of each category into a graph.  First, the plot exhibits rapid up-and-down variation.
We could not derive any trend from this variation. 
We smooth the plot using the simple moving average of order 4 on the data.  
We then plot the linear regression to fit the data.

\subsubsection{Time developer spend on a ticket }
When a developer work on the task assign to in a ticket, he spend time to analyse  the task. He then implement a solution and then test. The time spend analyzing and implementing the task assign in a ticket depend on the workload  of the ticket, the complexity of system, etc.  
We compute the average time spent by developers per month. 
The data also present rapid up-and-down variation, which we smooth with simple moving average of order 4. We use  linear regression to fit the data.   
\subsubsection{Average time  to test a ticket after development}
Generally, when a developer finishes a development related to a ticket, he tests his solution.  
The testing time is recorded in the ticket database.
 We use this information to compute the average per month of testing time. 
 \subsubsection{Team Manager time estimation}
For a ticket, the team manager estimates the time needed to finish the task related to the ticket.
This estimation is based on the experience of the team manager.  
We compare the time spent by the developer with the estimation per month over the life cycle of the system.  
This is to assess if the developer has enough time to develop good quality source code.
 We smooth data related to the comparisons and plot it to see the trend over the system life cycle.
 \section{Results and Discussion}\label{sec:results-discussion}

>>>>

	\section{Related Work}\label{sec:related-work}
	Research about software defect model for the reliable prediction of post-release defects in software is an ongoing and yet unresolved research topic. It was already discussed in multiple  publications \cite{Catal09,Hall2012, Hoss2017}. 
	Steffen Herbold \cite{Herb19} propose a cost model for software defect prediction
	These models aims to predict post-release defects but our model aims to fit  defects dataset  in order our reengineering on the studied system.   
	\section{Defect Model}\label{sec:defectModel}
	\subsection{Moving average}
	A moving average is a statistic technic usually used to smooth a time serie data and estimate it trend. The moving average of a period m is a series of consecutive averages of m terms at a time. The simple moving average is calculated as:

	\begin{equation}
	SMA_{t+1}=\frac{\sum\limits_{i=t-m}^t X_i}{m}
	\end{equation}
	\subsection{Presentation of the studied system}
	In general, legacy systems have a lifespan of several decades, decisions made at the beginning of development and their evolution over the life of the software are often lost. 
	This is the case of the studied system  which has a life cycle of  more than 20 years. 
	It has 3 MLOC software written in Powerbuilder. With 117 Powerbuilder library, the  bigest library is  over 300 KLOC.
	The system is not versioned and old versions are lost until 2012.

@@

	 \subsection{Experimentations}
	For each problem, we experiement on the ticket database. 
	\subsubsection{Avoid the system souce code lost}
	The system source code is not versioned.  Some versions of the system are lost. 
	When developers work in the same version of the system, they chat with each other to notify which part of the system they are modifying so that others won't modify the same part to avoid losing modifications. Besides, each developer has to write in a comment in the source code his name and the date in the form of each modification he made.  We believe that writing author in a comment in the source can be easily handled by a version control system.
	This is because of Powerbuilder support version controlling system from the 2017 release. 
	The support provided by Powerbuilder is not stable.
	The conflict resolution option is limited and a simple copy-paste of a library require a huge walkaround to update files. 
	With this constraint, we chose to start with a simple to use version controlling system. We introduce Apache Subversion. 
	 \subsubsection{Number of defects per library}
	We plot  defects and evolution per library over time.  In x axis we have years and in y axis  we have the number of defects  or evolutions.
	This give us an overview of defect  history per library. And  which libraries   trend to have defects.
	\subsubsection{ Average time to open and close a ticket}
	A ticket is closed when the task it is related to is done and validated. 
	We use the time a ticket remains open over the life cycle of the studied system as an indicator of the system state. 
	We grouped tickets by the month of creation.
	We then compute the average of  the duration between the time when the ticket is created and the time when the ticket is closed for each month.  
	We do this for tickets categorized as defect and tickets categorized as evolution. 
	We finally plot the result of each category into a graph.  First, the plot exhibits rapid up-and-down variation.
	We could not derive any trend from this variation. 
	We smooth the plot using the simple moving average of period 4 on the data.  
	We then plot the linear regression to fit the data.

	\subsubsection{Time developer spend on a ticket }
	When a developer work on the task assign to in a ticket, he spend time to analyse  the task. He then implement a solution and then test. The time spend analyzing and implementing the task assign in a ticket depend on the workload  of the ticket, the complexity of system, etc.  
	We compute the average time spent by developers per month. 
	The data also present rapid up-and-down variation, which we smooth with simple moving average of period 4. We use  linear regression to fit the data.   
	\subsubsection{Average time  to test a ticket after development}
	Generally, when a developer finishes a development related to a ticket, he tests his solution.  
	The testing time is recorded in the ticket database.
	 We use this information to compute the average per month of testing time. 
	 \subsubsection{Team Manager time estimation}
	For a ticket, the team manager estimates the time needed to finish the task related to the ticket.
	This estimation is based on the experience of the team manager.  
	We compare the time spent by the developer with the estimation per month over the life cycle of the system.  
	This is to assess if the developer has enough time to develop good quality source code.
	 We smooth data related to the comparisons and plot it to see the trend over the system life cycle.
	 \section{Results and Discussion}\label{sec:results-discussion}
